Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?

### 2016-06-29 text/ms.tex
done with all the plots and figures

%%\documentclass[12pt, preprint]{aastex}
\documentclass[12pt, preprint]{emulateapj}
\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{mathtools}
\usepackage{bm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\usepackage{algorithmic,algorithm}
\hypersetup{colorlinks}
\usepackage{color}
\usepackage{morefloats}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue}

@@

\begin{table*}
\begin{center}
  \label{tab:prior}
  \caption{{\bf Prior Specifications}: The prior probability distribution 
  and its range for each of the parameters. 
  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
\begin{tabular}{@{}lllll}
\\ \hline 
    HOD Parameter & & Prior & & Range \\ \hline
  $\alpha$ & & Uniform & & [0.85, 1.45] \\
  $\sigmam$ & & Uniform & &  [0.05, 1.5] \\
   $\mzero$   & & Uniform & &  [10.0, 14.5] \\
  $\mmin$ & &   Uniform & &  [10.0, 14.0] \\
  $\mone$ & & Uniform & & [11.5, 15.0] \\ 
  $\acen$ & & Uniform & & [-1.0, 1.0] \\
  $\asat$ & & Uniform & & [-1.0, 1.0] \\
 \hline
  \end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
  \label{tab:prior}
  \caption{{\bf Constraints}: The prior probability distribution 
  and its range for each of the parameters. 
  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
\begin{tabular}{@{}lllllllllllllllllllllllll}
\\ \hline 
    Model & & Observables & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
  \\
  Standard HOD & & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
   Heaviside-AB & & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $-$ & $-$ \\ \\

Standard HOD & & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ \\ \\

      Heaviside-AB & & $\gmf$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
       Heaviside-AB & & $\gmf$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
         Heaviside-AB & & $\wpp$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
           Heaviside-AB & & $\wpp$, $\bar{n}$ & 18.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
             Heaviside-AB & & $\wpp$, $\bar{n}$ & 19 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Heaviside-AB & & $\wpp$, $\bar{n}$ & 19.5 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Standard HOD & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\ \\
Heaviside-AB & & $\wpp$, $\bar{n}$ & 20 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ \\

>>>>

%%\documentclass[12pt, preprint]{aastex}
\documentclass[14pt, preprint]{emulateapj}
\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{mathtools}
\usepackage{bm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\usepackage{algorithmic,algorithm}
\hypersetup{colorlinks}
\usepackage{color}
\usepackage{morefloats}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue}

@@

\begin{table*}
\begin{center}
  \label{tab:prior}
  \caption{{\bf Prior Specifications}: The prior probability distribution 
  and its range for each of the parameters. 
  All mass parameters are in unit of $h^{-1}M_\odot$. The parameters marked by $*$ are only used in the Heaviside Assembly bias modeling.}
\begin{tabular}{@{}lllll}
\\ \hline 
    Parameter & & Prior & & Range \\ \hline
  $\alpha$ & & Uniform & & [0.85, 1.45] \\
  $\sigmam$ & & Uniform & &  [0.05, 1.5] \\
   $\mzero$   & & Uniform & &  [10.0, 14.5] \\
  $\mmin$ & &   Uniform & &  [10.0, 14.0] \\
  $\mone$ & & Uniform & & [11.5, 15.0] \\ 
  $\acen^{*}$ & & Uniform & & [-1.0, 1.0] \\
  $\asat^{*}$ & & Uniform & & [-1.0, 1.0] \\
 \hline
  \end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
  \label{tab:prior}
  \caption{{\bf Constraints}: The prior probability distribution 
  and its range for each of the parameters. 
  All mass parameters are in unit of $h^{-1}M_\odot$. The first five rows are the only parameters of the standard HOD modeling.}
\begin{tabular}{@{}lllllllllllllllllllllllll}
\\ \hline 
    Model & Data & $\mr$ & $\mmin$ & $\sigmam$ & $\mzero$ & $\alpha$ &  $\mone$ & $\acen$ & $\asat$ & $\chi^{2}/\rm{dof}$ & $\rm{AIC}$ & $\rm{BIC}$\\  \hline
  \\
  HOD & $\gmf$, $\bar{n}$ & 18 & $11.58^{+0.27}_{-0.22}$ &  $0.75^{+0.51}_{-0.48}$ & $10.93^{+0.68}_{-0.64}$ & $0.94^{+0.10}_{-0.07}$ &  $12.46^{+0.10}_{-0.09}$ & $-$ & $-$ & 5.55/1 & 21.55 & 19.42\\ \\

  AB & $\gmf$, $\bar{n}$ & 18 & $11.57^{+0.26}_{-0.20}$ &  $0.76^{+0.50}_{-0.50}$ & $10.83^{+0.65}_{-0.57}$ & $0.94^{+0.10}_{-0.06}$ &  $12.47^{+0.12}_{-0.09}$ & $0.13^{+0.63}_{-0.75}$ & $-0.01^{+0.60}_{-0.59}$ & 6.46/1 & 34.46 & 25.87\\ \\

HOD & $\gmf$, $\bar{n}$ & 19 & $11.87^{+0.32}_{-0.23}$ &  $0.70^{+0.53}_{-0.47}$ & $10.93^{+0.74}_{-0.65}$ & $0.99^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $-$ & $-$ & 5.19/1 & 18.72 & 20.87\\ \\

AB & $\gmf$, $\bar{n}$ & 19 & $11.88^{+0.31}_{-0.23}$ &  $0.74^{+0.50}_{-0.47}$ & $10.90^{+0.75}_{-0.62}$ & $0.97^{+0.10}_{-0.08}$ &  $12.73^{+0.07}_{-0.07}$ & $0.13^{+0.62}_{-0.73}$ & $-0.03^{+0.63}_{-0.59}$ & 6.66/1 & 28.13 & 28.61\\ \\

HOD  & $\gmf$, $\bar{n}$ & 20 & $12.16^{+0.36}_{-0.20}$ &  $0.58^{+0.50}_{-0.36}$ & $10.94^{+0.80}_{-0.66}$ & $0.98^{+0.09}_{-0.08}$ &  $13.07^{+0.07}_{-0.06}$ & $-$ & $-$ & 5.16/1 & 18.32 & 21.26\\ \\

AB  & $\gmf$, $\bar{n}$ & 20 & $12.14^{+0.34}_{-0.19}$ &  $0.56^{+0.47}_{-0.35}$ & $10.95^{+0.72}_{-0.64}$ & $0.96^{+0.10}_{-0.07}$ &  $13.08^{+0.07}_{-0.06}$ & $0.04^{+0.68}_{-0.70}$ & $-0.04^{+0.63}_{-0.58}$ & 6.04/1 & 26.63 & 28.57\\ \\

%%%%%%%wp%%%%%

HOD  & $\wpp$, $\bar{n}$ & 18 & $11.46^{+0.16}_{-0.17}$ &  $1.11^{+0.28}_{-0.47}$ & $10.85^{+0.74}_{-0.59}$ & $1.03^{+0.05}_{-0.06}$ &  $12.54^{+0.10}_{-0.10}$ & $-$ & $-$ & 31.72/13 & 50.29 & 44.55\\ \\

AB & $\wpp$, $\bar{n}$ & 18 & $11.44^{+0.15}_{-0.15}$ &  $1.20^{+0.21}_{-0.35}$ & $10.91^{+0.79}_{-0.64}$ & $1.02^{+0.06}_{-0.06}$ &  $12.61^{+0.11}_{-0.11}$ & $-0.82^{+0.27}_{-0.14}$ & $0.19^{+0.67}_{-0.73}$ & 31.81/13 & .55 & 19.42 \\ \\

HOD & $\wpp$, $\bar{n}$ & 18.5 & $11.64^{+0.23}_{-0.24}$ &  $0.89^{+0.43}_{-0.55}$ & $10.75^{+0.65}_{-0.51}$ & $1.06^{+0.05}_{-0.05}$ &  $12.72^{+0.09}_{-0.08}$ & $-$ & $0.37^{+0.44}_{-0.52}$ & 18.11/13 & 36.69 & 30.94\\ \\

AB & $\wpp$, $\bar{n}$ & 18.5 & $11.59^{+0.24}_{-0.21}$ &  $0.85^{+0.44}_{-0.54}$ & $10.77^{+0.63}_{-0.52}$ & $1.06^{+0.05}_{-0.06}$ &  $12.78^{+0.10}_{-0.10}$ & $-0.14^{+0.69}_{-0.56}$ & $0.37^{+0.44}_{-0.52}$ & 19.53/13 & 55.93 & 37.48\\ \\

HOD & $\wpp$, $\bar{n}$ & 19 & $11.84^{+0.28}_{-0.27}$ &  $0.89^{+0.41}_{-0.51}$ & $10.79^{+0.65}_{-0.54}$ & $1.08^{+0.04}_{-0.04}$ &  $12.89^{+0.09}_{-0.09}$ & $-$ & $-$ & 24.20/13 & 42.77 & 37.03\\ \\

AB & $\wpp$, $\bar{n}$ & 19 & $11.78^{+0.30}_{-0.24}$ &  $0.81^{+0.48}_{-0.51}$ & $10.77^{+0.66}_{-0.53}$ & $1.07^{+0.04}_{-0.05}$ &  $12.95^{+0.10}_{-0.10}$ & $0.15^{+0.52}_{-0.61}$ & $0.52^{+0.33}_{-0.44}$ & 22.80/13 & 59.20 & 40.75\\ \\

HOD & $\wpp$, $\bar{n}$ & 19.5 & $11.85^{+0.31}_{-0.19}$ &  $0.66^{+0.46}_{-0.40}$ & $10.88^{+0.67}_{-0.59}$ & $1.13^{+0.04}_{-0.04}$ &  $13.07^{+0.07}_{-0.07}$ & $-$ & $-$ & 15.89/13 & 34.46 & 28.72\\ \\

AB & $\wpp$, $\bar{n}$ & 19.5 & $11.82^{+0.38}_{-0.18}$ &  $0.63^{+0.55}_{-0.40}$ & $10.83^{+0.74}_{-0.57}$ & $1.10^{+0.04}_{-0.05}$ &  $13.07^{+0.08}_{-0.08}$ & $0.35^{+0.40}_{-0.52}$ & $0.03^{+0.59}_{-0.41}$ & 23.17/13 & 37.17 & 41.12\\ \\

HOD & $\wpp$, $\bar{n}$ & 20 & $11.99^{+0.15}_{-0.08}$ &  $0.36^{+0.28}_{-0.21}$ & $11.05^{+0.76}_{-0.71}$ & $1.17^{+0.04}_{-0.04}$ &  $13.34^{+0.07}_{-0.07}$ & $-$ & $-$ & 18.71/13 & 37.28 & 31.54\\ \\

AB & $\wpp$, $\bar{n}$ & 20 & $12.13^{+0.39}_{-0.18}$ &  $0.65^{+0.47}_{-0.38}$ & $11.14^{+0.80}_{-0.77}$ & $1.11^{+0.06}_{-0.06}$ &  $13.31^{+0.09}_{-0.09}$ & $0.71^{+0.21}_{-0.41}$ & $0.02^{+0.49}_{-0.33}$ & 15.22/13 & 51.62 & 33.17\\ \\
